Policing for Profit and the Mobilization of Black Voters

### 2021-04-07 markdown/draft_paper.tex
write

\title{Policing for Profit and the Mobilization of Black Voters}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Fines, Fees, and Turnout}
\author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jb4487@columbia.edu}{\nolinkurl{jb4487@columbia.edu}})} \and Kevin Morris\footnote{PhD Student, CUNY Graduate Center, Department of Sociology (\href{mailto:kmorris@gradcenter.cuny.edu}{\nolinkurl{kmorris@gradcenter.cuny.edu}})}}
\date{March 25, 2021}

@@

@@

\caption{\label{tab:balance-tab-chunk}\label{tab:balance} Balance Table}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lllllllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Means: Unmatched Data} & \multicolumn{2}{c}{Means: Matched Data} & \multicolumn{4}{c}{Percent Improvement} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-9}
 & Treated & Control & Treated & Control & Mean Diff & eQQ Med & eQQ Mean & eQQ Max\\
\midrule
\%White & 45.8\% & 47.4\% & 45.8\% & 45.8\% & 99.70 & 99.70 & 99.70 & 99.70\\
\% Black & 26.1\% & 23.0\% & 26.1\% & 26.1\% & 99.85 & 99.85 & 99.85 & 99.85\\
\% Latino & 19.1\% & 20.2\% & 19.1\% & 19.1\% & 99.97 & 99.97 & 99.97 & 99.97\\
\% Asian & 2.0\% & 2.3\% & 2.0\% & 2.0\% & 100.00 & 100.00 & 100.00 & 100.00\\
\% Male & 51.9\% & 50.8\% & 51.9\% & 51.2\% & 36.61 & 36.46 & 36.46 & 36.46\\
\% Democrat & 43.6\% & 41.6\% & 43.6\% & 43.3\% & 86.44 & 86.44 & 86.44 & 86.44\\
\% Republican & 22.9\% & 23.7\% & 22.9\% & 22.0\% & -5.57 & -5.57 & -5.57 & -5.57\\
Age & 42.7 & 42.4 & 42.7 & 42.2 & -67.69 & 11.98 & 33.08 & 70.35\\
Registration Date & 2006-09-25 & 2007-08-20 & 2006-09-25 & 2006-10-21 & 92.30 & 60.54 & 91.16 & 93.26\\
Stops in pre-period & 2.248 & 1.437 & 2.248 & 2.206 & 94.79 & 69.37 & 94.81 & 95.91\\
Turnout\textsubscript{t=-3} & 32.4\% & 28.4\% & 32.4\% & 32.5\% & 97.59 & 97.59 & 97.59 & 97.59\\
Turnout\textsubscript{t=-2} & 30.2\% & 27.5\% & 30.2\% & 30.2\% & 99.94 & 99.94 & 99.94 & 99.94\\
Turnout\textsubscript{t=-1} & 45.0\% & 38.2\% & 45.0\% & 45.0\% & 99.97 & 99.97 & 99.97 & 99.97\\
Median Income & \$62,193 & \$63,412 & \$62,193 & \$62,111 & 93.27 & 82.89 & 79.16 & 68.07\\
\% with Some College & 73.8\% & 74.4\% & 73.8\% & 73.9\% & 78.57 & 53.38 & 57.55 & 53.15\\
Unemployment Rate & 6.7\% & 6.5\% & 6.7\% & 6.6\% & 49.02 & -19.29 & -20.95 & -17.34\\
\bottomrule
\end{tabular}}
\end{table}
\end{singlespace}

>>>>

\title{Policing for Profit and the Mobilization of Black Voters}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Fines, Fees, and Turnout}
\author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jb4487@columbia.edu}{\nolinkurl{jb4487@columbia.edu}})} \and Kevin Morris\footnote{PhD Student, CUNY Graduate Center, Department of Sociology (\href{mailto:kmorris@gradcenter.cuny.edu}{\nolinkurl{kmorris@gradcenter.cuny.edu}})}}
\date{April 07, 2021}

@@

\begin{gather}
\label{eq:1}
v_{it}=\beta_0+\beta_1Treated_{i}+\beta_2Election Following Stop_{t} + \nonumber \\
\beta_3Treated_{i}\times Election Following Stop_{t} + \\
\delta{Z}_{i} + \mathcal{E}_{it}. \nonumber
\end{gather}

@@

\caption{\label{tab:balance-tab-chunk}\label{tab:balance} Balance Table}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lllllllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Means: Unmatched Data} & \multicolumn{2}{c}{Means: Matched Data} & \multicolumn{4}{c}{Percent Improvement} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-9}
 & Treated & Control & Treated & Control & Mean Diff & eQQ Med & eQQ Mean & eQQ Max\\
\midrule
\%White & 47.3\% & 49.1\% & 47.3\% & 47.4\% & 97.14 & 97.14 & 97.14 & 97.14\\
\% Black & 24.4\% & 21.0\% & 24.4\% & 24.4\% & 99.93 & 99.93 & 99.93 & 99.93\\
\% Latino & 19.1\% & 20.2\% & 19.1\% & 19.5\% & 61.05 & 61.06 & 61.06 & 61.06\\
\% Asian & 2.1\% & 2.4\% & 2.1\% & 2.1\% & 99.55 & 99.55 & 99.55 & 99.55\\
\% Male & 53.2\% & 52.4\% & 53.2\% & 53.8\% & 19.36 & 19.66 & 19.66 & 19.66\\
\% Democrat & 42.5\% & 40.0\% & 42.5\% & 42.4\% & 97.61 & 97.61 & 97.61 & 97.61\\
\% Republican & 23.6\% & 24.5\% & 23.6\% & 23.2\% & 54.62 & 54.62 & 54.62 & 54.62\\
Age & 42.3 & 41.5 & 42.3 & 41.8 & 36.76 & -135.34 & 29.65 & 71.41\\
Registration Date & 2006-11-05 & 2007-12-11 & 2006-11-05 & 2007-01-04 & 84.91 & 78.16 & 79.83 & 72.00\\
Stops in pre-period & 2.163 & 1.433 & 2.163 & 2.125 & 94.77 & 53.17 & 94.78 & 97.18\\
Turnout\textsubscript{t=-3} & 31.9\% & 27.4\% & 31.9\% & 31.9\% & 99.89 & 99.89 & 99.89 & 99.89\\
Turnout\textsubscript{t=-2} & 29.3\% & 26.7\% & 29.3\% & 29.3\% & 99.87 & 99.87 & 99.87 & 99.87\\
Turnout\textsubscript{t=-1} & 44.9\% & 37.5\% & 44.9\% & 44.9\% & 99.85 & 99.85 & 99.85 & 99.85\\
Median Income & \$62,832 & \$64,169 & \$62,832 & \$62,642 & 85.81 & 71.32 & 67.46 & 55.93\\
\% with Some College & 73.9\% & 74.5\% & 73.9\% & 74.0\% & 88.43 & 46.05 & 53.04 & 45.74\\
Unemployment Rate & 6.6\% & 6.4\% & 6.6\% & 6.5\% & 29.50 & -25.47 & -14.60 & -3.97\\
\bottomrule
\end{tabular}}
\end{table}
\end{singlespace}
